---
title: "p8105_hw1_fc2691"
author: "FC"
date: "9/25/2021"
output: 
  github_document:
    toc: true
---


## Problem 1 

### Create a Data Frame
  
*This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.*  

```{r}
#Create a random sample of size 10 from a standard Normal distribution
random_list <- rnorm(10, 0, 1)  

# Make elements of the sample are greater than 0
positive_elements <- random_list > 0  

#Create data frame containing variables
df <- data.frame(
  random = random_list,
  pov = positive_elements,
  char = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("a","b","c","a","b","c","a","b","c","a"))
)
df
mean(df$random)
mean(df$pov)
mean(df$char)
mean(df$factor_vec)
```

### Calculate Mean  

***Requirement***: *Take the mean of a variable in a dataframe, pull the variable out of the dataframe. Try loading the tidyverse and using the pull function.*  

```{r}
library(tidyverse)

df %>%
  pull(var = 1) %>% 
  mean()

mean_pov = mean(pull(df, var = 2))
mean_pov
```

- **What is the mean of each variable in your dataframe? What works and what doesn’t?**  
R could calculate the mean of numeric variables.  
R would treat "TRUE" as 1 and "FALSE" as 0, and then calculate the mean of that list.  
Mean doesn't work for characters and factors.  

- **Convert variables from one type to another**  
*Write a code chunk that applies the **as.numeric** function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?*

```{r, eval=FALSE}
as.numeric(positive_elements)
is.numeric(positive_elements)
as.numeric(c("a","b","c","d","e","f","g","h","i","j")) 
as.numeric(factor(c("a","b","c","a","b","c","a","b","c","a")))
is.numeric(factor(c("a","b","c","a","b","c","a","b","c","a")))
is.numeric(as.numeric(factor(c("a","b","c","a","b","c","a","b","c","a"))))
```
Got "Warning" message when applied "as.numeric" function to character variables. So character cannot be calculated as numeric or change to numeric. However, as.numeric() could change factors, with its three levels, to corresponded numbers and mean can then be calculated. Same it could change the logic "TRUE" and "FALSE" to number 1 and 0. While logic and factors themselves are still not numeric. 

## Problem 2  

### Analyze Data in Package "palmerpenguins"  

Install.packages("palmerpenguins")  


*Use the following code (in your RMarkdown file) to load the penguins dataset. * 

```{r, eval=FALSE}

library(tidyverse)
data("penguins", package = "palmerpenguins")

penguins
summary(penguins)
names(penguins)
nrow(penguins)
ncol(penguins)
dim(penguins)


penguins_omit = na.omit(penguins)
mean(pull(penguins_omit, var = "flipper_length_mm"))

```
The **penguins** dataset includes 344 rows and 8 columns. It decribes the species on island with the data about their bill length, bill depth and flipper length in mm. It also contains some "NA" which means data is missing. The mean number of flipper_length is about 200 mm.    

### Making a Scatterplot  

*Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help). And export your first scatterplot to your project directory using ggsave.*

```{r}

data("penguins", package = "palmerpenguins")
penguins_omit = na.omit(penguins)
ggplot(penguins_omit, aes(bill_length_mm, flipper_length_mm, colour = species)) + geom_point()

ggsave("./Scatterplot of penguins.pdf")
```




